Importing data
```{r}
library(MASS)
drivers_df <- drivers
hist(drivers_df)
```
Plotting Emperical Distribution
```{r}
library(MASS)
drivers_df <- drivers
drivers_df.ecdf <- ecdf(drivers_df)
plot.ecdf(drivers_df,xlab = "Deaths")
```
Point estimation of Median

```{r}
th.hat <- median(drivers_df)
print(th.hat)
```

Non parametric bootstrap to find Confidence Interval of the Median 

```{r}
library(bootstrap)

theta <- function(x, xdata)
{
  median(xdata[x])
}
n = length(drivers_df)

drivers_df.boot <- bootstrap(1:n,3200,theta, drivers_df)

Dboot<-drivers_df.boot$thetastar #vector of bootstrap results
se.boot <- sqrt(var(Dboot))

Normal_CI <- c(th.hat - 2*se.boot, th.hat + 2*se.boot)
print("Normal CI = ")
print(Normal_CI)

Pivotal_CI <- c(2*th.hat-quantile(Dboot,.975),2*th.hat-quantile(Dboot, .025))
print("Pivotal CI = ")
print(Pivotal_CI)

Quantile_CI <- c(quantile(Dboot,.025), quantile(Dboot,.975))
print("Quantile CI = ")
print(Quantile_CI)
```
Parametric Estimation
```{r}

mu_hat <- mean(drivers_df)
sigma_hat = sd(drivers_df)*sqrt(n/(n-1))
tau_hat <- mu_hat + qnorm(0.5) * sigma_hat
print(tau_hat)
```
CI using  parametric bootstrap
```{r}
##parametric bootstrap
tau_bootstrap <- vector()

for(i in 1:1000)
  {
  X = rnorm(n,mu_hat,sigma_hat)
  X_mu = mean(X)
  X_sigma = sd(X)*(sqrt(n/(n-1)))
  tau_bootstrap[i] = X_mu + qnorm(0.5)*X_sigma
  }
tau_bootstrap_se <- sd(tau_bootstrap)
tau_bootstrap_se
```


```{r}
#CI
normal_ci <- c(mu_hat - 2 * tau_bootstrap_se, mu_hat + 2 * tau_bootstrap_se)
print(normal_ci)
```
#We will test for hypothesis that the proportion of deaths over the years are the same 
```{r}
deaths_yearly <- vector()
prob = vector()
#yearly deaths for 16 years
for(i in 1:16)
{
  p = (i-1)*12 + 1
  q = i*12
  deaths_yearly[i] = sum(drivers_df[p:q])
  prob[i] = (1/16)
}
chisq.test(x= deaths_yearly,p=prob)
```
For alpha = 0.05, we can rejct the null hypothesis that the proportion of deaths are same yearly 

We can also test for an important hypothesis whether the introduction of seatbelts in UK after 31st Jan 1983 (as given in the data description) resulted in less accidents
```{r}
drivers_before_sb <- drivers_df[1:169]
drivers_after_sb <- drivers_df[170:192]
par(mfrow=c(1,2))
hist(drivers_before_sb)
hist(drivers_after_sb)
X = mean(drivers_before_sb)
Y = mean(drivers_after_sb)
Sx = sd(drivers_before_sb)*168/169
Sy = sd(drivers_after_sb)*22/23
Z = (X - Y)/((Sx^2/169)+(Sy^2/23))
p_value = 1-pnorm(abs(Z))
print(p_value)
```
Since the p-value is greater than alpha (0.05) we reject the null hypothesis. Therefore, we conclude the mean of normal distribution after the introduction of seatbelt compulsion rule is more.